Modeling the Circumnuclear Mediums and Accetion Rates of Quiescent Supermassive Black Holes

### 2015-01-09 ms.tex
test

\author[Generozov, Stone, \& Metzger]{Aleksey Generozov$\thanks{E-mail: ag@astro.columbia.edu}$, Nicholas Stone, Brian~D.~Metzger\\
  Columbia Astropysics Labratory, Columbia University, 550 West 120th Street, New York, NY 10027}

@@

\begin{abstract}
  We calculate the steady-state hydrodynamic profiles of hot gas in
  the nuclei of a sample of early-type quiescent galaxies.  We assume
  that mass is supplied to the circumnuclear medium (CNM) entirely by
  stellar winds according to the radial stellar profiles for each
  galaxy, while the gas is heated by a combination of shocked stellar
  winds and supernovae.  Our analytic and numerical results are used
  to estimate the accretion rates onto the central supermassive black
  holes (SMBH) as a function of the SMBH mass $M_{\bullet}$ and the
  heating efficiency, the latter of which is related schematically to
  the age of the stellar population, the frequency of supernovae, and
  the efficacy of accretion feedback processes.  For a fixed heating
  efficiency, we find that the SMBH accretion Eddington factor
  increases with the SMBH mass, $\dot{M}/\dot{M}_{\rm edd} \propto
  M_{\bullet}^{\alpha}$ with $\alpha \approx 0.5, 1$ for cusp and core
  nuclei, respectively.
  % However, considering the potentially lower heating efficiency of low
  % mass SMBHs (due to a younger stellar population and the rareity of
  % supernovae within the stagnation radius) and their resulting higher
  % susceptibility to cooling instability, we find a flatter
  % relationship $\alpha \approx 0$. 
  Our results are used to check previous estimates of the SMBH
  accretion rate assuming Bondi accretion and extrapolating the X-ray
  measured density and temperature to the unresolved Bondi radius.  We
  also discuss the implications of our results for the diversity of
  CNM environments encountered by the jetted outflows from tidal
  disruption events, and for the use of an assumed
  $\dot{M}-M_{\bullet}$ relationship to constrain the occupation
  fraction of SMBHs in low mass galaxies.
\end{abstract}

>>>>

\author[Generozov, Stone, \& Metzger]{Aleksey S.~Generozov$\thanks{E-mail: ag@astro.columbia.edu}$, Nicholas Stone, Brian~D.~Metzger\\
  Columbia Astropysics Labratory, Columbia University, 550 West 120th Street, New York, NY 10027}

@@

\begin{abstract}
  Steady-state hydrodynamic profiles of hot gas in  the nuclei of a sample of early-type quiescent galaxies are calculated.  We assume
  that mass is supplied to the circumnuclear medium (CNM) entirely by
  stellar winds according to the radial stellar profiles for each
  galaxy, while the gas is heated by a combination of shocked stellar
  winds and supernovae.  Our analytic and numerical results are used
  to estimate the accretion rates onto the central supermassive black
  holes (SMBH) as a function of the SMBH mass $M_{\bullet}$ and the
  heating efficiency, the latter of which is related schematically to
  the age of the stellar population, the frequency of supernovae, and
  the efficacy of accretion feedback processes.  For a fixed heating
  efficiency, we find that the SMBH accretion Eddington factor
  increases with the SMBH mass, $\dot{M}/\dot{M}_{\rm edd} \propto
  M_{\bullet}^{\alpha}$ with $\alpha \approx 0.5, 1$ for cusp and core
  nuclei, respectively.
  % However, considering the potentially lower heating efficiency of low
  % mass SMBHs (due to a younger stellar population and the rareity of
  % supernovae within the stagnation radius) and their resulting higher
  % susceptibility to cooling instability, we find a flatter
  % relationship $\alpha \approx 0$. 
  Our results are used to check previous estimates of the SMBH
  accretion rate assuming Bondi accretion and extrapolating the X-ray
  measured density and temperature to the unresolved Bondi radius.  We
  also discuss the implications of our results for the diversity of
  CNM environments encountered by the jetted outflows from tidal
  disruption events, and for the use of an assumed
  $\dot{M}-M_{\bullet}$ relationship to constrain the occupation
  fraction of SMBHs in low mass galaxies.
\end{abstract}
